Increasing User Engagement in a Volunteer-Based Ephemeral Evolutionary Computation System

### 2017-11-08 2017-EUROPAR/Gamification/paper.tex
Rewriting the introductory paragraph
And also adding a bit. Please @mariosky check it out.

There is a trade-off between ease of use, where users just need to visit a web page, versus personlaization, where users need to register and subsecuently authenticate in order to participate. Registration could be seen as a barrier to volunteers trying to participate in an ephemeral experiment, so the question is what is the impact on user participation.

>>>>

There is a trade-off between ease of use, allowing users to
participate by just visiting a web page, and personalization, making
registration compulsory and subsequently authenticate in order to
participate. In a sociotechnical system such as this one, every
decision the user has to take has an influence on the overall
performance, and registration could be seen as a hurdle to volunteers
trying to participate in an ephemeral experiment, so it is a challenge
to analyze what actually happens in this case; this is one of the main
questions addressed in this paper.
